Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)

### 2012-08-21 paper2.tex
more edits.  Filling in the covering Lemma now.

\begin{lemma}\label{lem:epslmlemma}
Both $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$.
\end{lemma}
\begin{IEEEproof}
We prove the lemma for $d_2$.  The proof for $d_1$ is similar.  Observe that $d_2(\lambda, 0) = c_1 + c_2$ where 
 \[
 c_1 = \sum_{i \in P} R_i\sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i) }
 \]
 and 
 \[
 c_2 = \sum_{i \in D} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 As $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
 \[
 \sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i)} \leq K\sabs{\lambda} = \sabs{\lambda} < \epsilon
 \]
 for all $i \in P \cup D$, and therefore $c_1 \leq \epsilon \sum_{i \in P} R_i$.  Let $S = \{ i \in D \mid I_\epsilon(\Phi_i) = 1\}$. Now $c_2 = c_3 + c_4$ where 
 \[
 c_3 = \sum_{i \in D, i \in S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}
 \]
 and
 \[
 c_4 =  \sum_{i \in D, i \notin S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 If $i \notin S$ then $\round{\lambda + \Phi_i} = \round{\Phi_i}$ for all $\sabs{\lambda} < \epsilon$ and therefore
 \begin{align*}
 \vert\sin&\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}\vert \\
 &= \sabs{\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\Phi_i - \round{\Phi_i})} \\
 &\leq \sabs{\lambda} < \epsilon
 \end{align*}
and so, 
\[
c_4 \leq \epsilon \sum_{i \in D, i \notin S} R_i \leq \epsilon \sum_{i \in D} R_i.
\]
Otherwise, if $i \in S$, then $\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}} \leq 2$ because $\sin(\cdot) \leq 1$.  Thus 
\[
c_3 \leq 2 \sum_{i \in D, i \in S} R_i \leq 2 \sum_{i \in P \cup D} R_i I_\epsilon(\Phi_i).
\]
Now,
\begin{align*}
d_2(\lambda, 0) &= c_1 + c_2 \\
&\leq c_1 + c_3 + c_4 \\
&\leq \epsilon \sum_{i \in P \cup D} R_i + 2 \sum_{i \in P \cup D} R_i I_\epsilon(\Phi_i) \\
&= D_\epsilon L
\end{align*}
as required
\end{IEEEproof}

@@

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are zero mean Gaussian random variables each with variance less than some positive constant $K$.  Then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}

\begin{lemma}\label{lem:metricentropy}(Covering numbers)
For $k \in \ints$ there exists a discrete set $T_\epsilon(k) \subset B_\epsilon$ with the property that, for every $\lambda \in B_\epsilon$, there is a $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L,
\]
where $C_\epsilon$ and $D_\epsilon$ are defined in~\eqref{eq:Cepsdefn} and~\eqref{eq:Depsdefn}.  The number of elements in $T_\epsilon(k)$ is no more than $K_3 2^{k}$ where $K_3$ is a positive constant, independent of $L$, $\epsilon$ and $k$.
\end{lemma}
\begin{IEEEproof}

>>>>

\begin{lemma}\label{lem:epslmlemma}
Both $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$.
\end{lemma}
\begin{IEEEproof}
We prove the lemma for $d_2$.  The proof for $d_1$ is similar.  Observe that $d_2(\lambda, 0) = c_1 + c_2$ where 
 \[
 c_1 = \sum_{i \in P} R_i\sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i) },
 \] 
 \[
 c_2 = \sum_{i \in D} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 As $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
 \[
 \sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i)} \leq K\sabs{\lambda} = \sabs{\lambda} < \epsilon
 \]
 for all $i \in P \cup D$, and therefore $c_1 \leq \epsilon \sum_{i \in P} R_i$.  Let 
\[
S = \{ i \in D \mid I_\epsilon(\Phi_i) = 1\}.
\] 
Now $c_2 = c_3 + c_4$ where 
 \[
 c_3 = \sum_{i \in D, i \in S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}},
 \]
 \[
 c_4 =  \sum_{i \in D, i \notin S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
Observe that $I_\epsilon(\Phi_i) = 1$ if and only if $\abs{\fracpart{\Phi_i}} \geq \tfrac{\pi}{M} - \epsilon$.  So, if $i \notin S$ and $\sabs{\lambda} < \epsilon$, then
\begin{align*}
\round{\lambda + \Phi_i} &= \round{\lambda + \fracpart{\Phi_i} + \round{\Phi_i}} \\ 
&= \round{\lambda + \fracpart{\Phi_i}} + \round{\Phi_i} = \round{\Phi_i}
\end{align*}
because
\[
\sabs{\lambda + \fracpart{\Phi_i}} < \epsilon + \tfrac{\pi}{M} - \epsilon = \tfrac{\pi}{M}
\] 
and therefore $\round{\lambda + \fracpart{\Phi_i}} = 0$.  Now,
 \begin{align*}
 \vert\sin&\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}\vert \\
 &= \sabs{\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\Phi_i - \round{\Phi_i})} \\
 &\leq \sabs{\lambda} < \epsilon
 \end{align*}
and so, 
\[
c_4 \leq \epsilon \sum_{i \in D, i \notin S} R_i \leq \epsilon \sum_{i \in D} R_i.
\]
Otherwise, if $i \in S$, then $\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}} \leq 2$ because $\sin(\cdot) \leq 1$.  Thus 
\[
c_3 \leq 2 \sum_{i \in D, i \in S} R_i \leq 2 \sum_{i \in P \cup D} R_i I_\epsilon(\Phi_i).
\]
Now,
\begin{align*}
d_2(\lambda, 0) &= c_1 + c_2 = c_1 + c_3 + c_4 \\
&\leq \epsilon \sum_{i \in P \cup D} R_i + 2 \sum_{i \in P \cup D} R_i I_\epsilon(\Phi_i) = D_\epsilon L
\end{align*}
as required
\end{IEEEproof}

@@

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are zero mean Gaussian random variables each with variance less than some positive constant $K$, then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}

\begin{lemma}\label{lem:metricentropy}(Covering numbers)
For $k \in \ints$ there exists a discrete set $T_\epsilon(k) \subset B_\epsilon$ with the property that, for every $\lambda \in B_\epsilon$, there is a $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L,
\]
where $C_\epsilon$ and $D_\epsilon$ are defined in~\eqref{eq:Cepsdefn} and~\eqref{eq:Depsdefn}.  The number of elements in $T_\epsilon(k)$ is no more than $K_3 2^{k}$ where $K_3$ is a positive constant, independent of $L$, $\epsilon$ and $k$.
\end{lemma}
\begin{IEEEproof}
We will first construct a set $T^2_\epsilon(k)$ containing no more than $K_{23}2^{k}$ elements and so that for every $\lambda \in B_\epsilon$ there exists $\lambda_2 \in T^2_\epsilon(k)$ such that $d_2(\lambda, \lambda_2) \leq 2^{-k} D_\epsilon L$ with $K_{23}$ a constant, independent of $L$, $\epsilon$ and $k$.  Using a similar construction we find a set $T^1_\epsilon(k)$ containing no more than $K_{13}2^{k}$ elements and so that for every $\lambda \in B_\epsilon$ there exists $\lambda_1 \in T^1_\epsilon(k)$ such that $d_1(\lambda, \lambda_2) \leq 2^{-k} D_\epsilon L$ with $K_{13}$ a constant, independent of $L$, $\epsilon$ and $k$.  Puting $T_\epsilon(k) = T^1_\epsilon(k) \cup T^2_\epsilon(k)$ will then complete the proof with $K_3 = K_{13} + K_{23}$.

We will only give a construction for $T^2_\epsilon(k)$, the construction for $T^1_\epsilon(k)$ being similar.  First observe that
\[
f_{i}(\lambda) - f_{i}(\lambda_2) = \begin{cases}
R_i\big( \sin(\lambda + \Phi_i) - \sin(\lambda_2 + \Phi_i) \big) & i \in P \\
R_i\big(\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda_2 + \Phi_i}\big) & i \in D
\end{cases}
\]
Let 
\[
U = \{\epsilon(\ell 2^{-k} - 1) \mid \ell = 0, 1, \dots, 2^{k+1} \} 
\]
be a set containing $2^{k+1} + 1$ elements uniformly spaced over $B_\epsilon$.  For every $\lambda \in B_\epsilon$ there exists a $\lambda^* \in U$ such that $\abs{\lambda - \lambda^*} < \epsilon 2^{-k}$.  Since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$, it follows that if $i \in P$ then,
Let 
\begin{align*}
\abs{f_{i}(\lambda) - f_{i}(\lambda_2)} &= R_i\abs{ \sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i) } \\
&\leq R_i\sabs{\lambda - \lambda^*} \\
&< \epsilon 2^{-k} R_i.
\end{align*}
Thus
\[
\sum_{i \in P} \sabs{f_{i}(\lambda) - f_{i}(\lambda^*)} < \epsilon 2^{-k} \sum_{i\in P} R_i.
\]
As in Lemma~\ref{lem:epslmlemma} let $S = \{ i \in D \mid I_\epsilon(\Phi_i) \}$. Now, if $i \in D$ but $i \notin S$ then 
\[
\round{\lambda + \Phi_i} = \round{\lambda^* + \Phi_i} = \round{\Phi_i},
\] 
so
 \begin{align*}
 \vert &f_{i}(\lambda) - f_{i}(\lambda_2)\vert \\
&= R_i\vert\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda^* + \Phi_i}\vert \\
 &= R_i\vert\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\lambda^* + \Phi_i - \round{\Phi_i})\vert  \\
 &\leq R_i \sabs{\lambda - \lambda^*} \\
&< \epsilon 2^{-k} R_i.
 \end{align*}
Thus,
\[
\sum_{i \in D, i \notin S} \sabs{f_{i}(\lambda) - f_{i}(\lambda^*)} < \epsilon 2^{-k} \sum_{i \in D, i \notin S} R_i \leq \epsilon 2^{-k} \sum_{i \in D} R_i
\]

To handle the case when $i \in S$ we need to add some extra elements to the set $U$.  Let $\sigma$ be a permutation of the indices in $S$ such that $\fracpart{\Phi_i}$ are in ascending order.
